Deep learning for geophysics

### 2023-09-22 manuscript.tex
Merge branch 'main' into paper2

\chapter{Magnetic Grid Resolution Enhancement using Machine Learning}
This chapter has been reproduced from the following peer reviewed publication. Formatting has been adjusted for consistency.

@@

\chapter{A Line Spacing Method for Super-resolution of Geophysical Surveys}
% \subfile{paper2}

\chapter{Implicit Neural Representation for Potential Field Geophysics}
% \subfile{paper3}

>>>>

\chapter{Magnetic Grid Resolution Enhancement using Machine Learning}
\label{paper1}
This chapter has been reproduced from the following peer reviewed publication. Formatting has been adjusted for consistency.

@@

\chapter{A Line Spacing Method for Super-resolution of Geophysical Surveys}
\label{paper2}
% \subfile{paper2}

\chapter{Implicit Neural Representation for Potential Field Geophysics}
\label{paper3}
% \subfile{paper3}
